Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-03-18 ms.tex
rearranging

\subsection{Smoothing}
\label{sec:smth}
For our full-resolution model,  wish to simultaneously fit \verb|i100| along 
with the four highest-frequency \PLANCK~bands. To properly combine these maps, 
they must have the same point spread function (PSF). \verb|i100|, with its 
$6.1'$ symmetric Gaussian beam, has the lowest angular resolution of the 
relevant maps. To match PSFs, we have therefore smoothed each of the 
\PLANCK~maps under consideration to $6.1'$ resolution by considering each 
native map to have a symmetric Gaussian beam and smoothing by the appropriate 
symmetric Gaussian such that the resulting map has a FWHM of $6.1'$. The FWHM 
we assign to the native \PLANCK~maps is taken from \cite{planckbeam}, 
specifically $5.01'$ for 217 GHz, $4.86'$ for 353 GHz, $4.84'$ for 545 GHz, and
$4.63'$ for 857 GHz.

@@

\subsection{Molecular Emission}
One advantage of the FIRAS data used by FDS99 was its many narrow bins in 
frequency, which allowed those frequency ranges contaminated by strong 
molecular line emission to be discarded from the analysis. Unfortunately, with 
the broad \PLANCK~and \IRAS~bandpasses we do not have such a luxury. This means
 that we cannot truly separate out the thermal continuum of dust emission we 
wish to study from the molecular line emission. The most prominent molecular 
line emission in the Planck bands of interest arises from CO lines in the XX, 
YY bands. We investigated the possibility of subtracting out CO emission based 
on the template of \cite{planckco}. However, we found that the CO emission
rarely amounted to more than XX\% of the total intensity, and following
the treatment of \cite{planckdust}, $\S$2.1, we do not attempt to remove CO
emission.

@@

@@

>>>>

\subsection{Smoothing}
\label{sec:smth}
For our full-resolution model, we wish to simultaneously fit \verb|i100| along 
with the four highest-frequency \PLANCK~bands. To properly combine these maps, 
they must have the same point spread function (PSF). \verb|i100|, with its 
$6.1'$ symmetric Gaussian beam, has the lowest angular resolution of the 
relevant maps. To match PSFs, we have therefore smoothed each of the 
\PLANCK~maps under consideration to \verb|i100| resolution by considering each 
native \PLANCK~map to have a symmetric Gaussian beam and smoothing by the 
appropriate symmetric Gaussian such that the resulting map has a  $6.1'$ FWHM. 
The FWHM we assign to the native \PLANCK~maps is taken from \cite{planckbeam}, 
specifically $5.01'$ for 217 GHz, $4.86'$ for 353 GHz, $4.84'$ for 545 GHz, and
 $4.63'$ for 857 GHz.

\subsection{Molecular Emission}
Because the FIRAS spectra consist of many narrow frequency bins, FDS99 were
able to discard the relatively small number of frequency intervals contaminated
by strong molecular line emission. Unfortunately, while the \PLANCK~data 
considered in this study are of high angular resolution, their broad bandpasses
do not offer the same luxury of spectral resolution in dealing with line 
emission. Thereore, we must subtract estimates of the molecular line 
contamination from each band in order to best isolate the thermal continuum we 
wish to characterize. The most prominent molecular line emission in the
\PLANCK~bands of interest arises from the three lowest CO rotational
transitions: J=1$\rightarrow$0 at 115 GHz, J=2$\rightarrow$1 at 230 GHz and 
J=3$\rightarrow$2 at 345 GHz, respectively affecting the \PLANCK~100, 217 and 
353 GHz bands.

%We investigated the possibility of subtracting out CO emission 
%based on the template of \cite{planckco}. However, we found that the CO 
%emission rarely amounted to more than XX\% of the total intensity, and 
%following the treatment of \cite{planckdust}, $\S$2.1, we do not attempt to 
%remove CO emission.

%We did not attempt to correct for higher J CO transitions beyond J=3->2

@@

@@

% add error bars to this example SED plot

@@

% overplot ellipses showing 1 sigma errors in posterior grayscales
